% Second example from documentation, slightly modified to use Ingredient, too
% https://ftp.agdsn.de/pub/mirrors/latex/dante/macros/latex/contrib/cuisine/cuisine.pdf

\begin{recipe}[Zabaglione]{Zabaglione alla Marsala}{4 Portions}{\fr12 hour}
\freeform This is a well-known Italian recipe which is
great for piling on the calories.
\ingredient[6]{}{egg yolks}
\ingredient[2]{oz}{granulated sugar}
\ingredient[6--8]{tbsp}{Marsala (or sherry)}
\ingredient[\fr14]{oz}{gelatine}
\ingredient[2]{tbsp}{cold water}
In the top of a double boiler, combine the egg yolks with sugar and
Marsala, and whip the mixture over hot, but not boiling, water until it
thickens. Stir in gelatine, softened in cold water and dissolved over hot
water.
\ingredient[3]{tbsp}{brandy}
\ingredient[\fr38]{pt}{double cream}
Put the pan in a bowl of ice and stir the
zabaglione well until it is thick and free of bubbles. When it is almost
cold, fold in brandy and whipped cream and pour into individual moulds.
\freeform\rule{\textwidth}{0.05pt}\newpage
\freeform\rule{\textwidth}{0.05pt}
\ingredient[3]{}{egg yolks}
\ingredient[1]{oz}{granulated sugar}
\Ingredient{granulated sugar}
\ingredient[3--4]{tbsp}{Marsala (or sherry)}
\ingredient[1\fr12]{tbsp}{brandy}
To make the sauce, combine egg yolks and sugar in the top of a double
saucepan. Whisk mixture over hot, but not boiling, water until the
sauce coats
the back of a spoon. Stir in the Marsala and brandy.
\newstep
Chill the zabaglione, unmould it, and serve with the sauce immediately.
\freeform\hrulefill
\end{recipe}
